---
title: "MCMC Code for sampling from posterior t distribution"
author: "Eric Folsom"
format: pdf
---

```{r}
#| label: setup
#| echo: true
#| warning: false
library(tidyverse)
library(brms)
library(janitor)
set.seed(502)
```

We are trying to create a posterior distribution for the degrees of freedom from a $t$ distribution. We can set up our model as follows:

Our likelihood, or sampling distribution is:

$$
p(y_i | t) \sim t(\nu)
$$


For our prior we have a couple of choices:
$$
p(\nu) \sim \text{Some strictly positive distribution}
$$

For our prior for $\nu$ we will try the following:

$$
p(\nu) \sim \text{Uniform}(0,\theta) \text{with various choices of } \theta
$$

$$
p(\nu)\sim N^+(0,\sigma^2) \quad \text{with various choices of } \sigma^2
$$

$$
p(\nu)\sim \text{Gamma}(\alpha, \beta) \text{with various choices of } \alpha \text{ and } \beta
$$

$$
p(\nu)\sim \text{Cauchy}^+()
$$

Thus our model for our posterior, $P(\nu | y_i)$ will be 

$$
P(\nu|y_i)\propto p(\mathbf{y} | \nu) p(\nu)
$$


We can generate data from $t$-distributions with various degrees of freedom ($\nu$) as follows:

```{r}
#| label: simulate_data
#| echo: true
#| warning: false
# function to simulate data from a t-distribution

set.seed(502)
sim_dat <- function(nsims, nu) {
  cols <- nu |>
    map(function(nu) {
      rt(nsims, nu)
    })

  names(cols) <- paste0("nu_", nu)

  data <- as.data.frame(cols)

  return(data)
}

# select 5 different values of nu from 2-25 to simulate data from
nu <- sample(c(2:25), 5, replace = F) |> sort()
dat_100000 <- sim_dat(100000, nu) # simulate the data
dat_10000 <- sim_dat(10000, nu) # simulate the data
dat_1000 <- sim_dat(1000, nu) # simulate the data
dat_100 <- sim_dat(100, nu) # simulate the data

sprintf(
  "We are trying the following values of nu: %s, %s, %s, %s, %s",
  nu[1],
  nu[2],
  nu[3],
  nu[4],
  nu[5]
)
```

```{r}
#| label: setup_mcmc
#| echo: true
#| warning: false
prior_uniform_1_50 <- prior(uniform(1, 50), class = "nu", lb = 1, ub = 50)
prior_gamma_1_4 <- prior(gamma(1, 4), class = "nu")
prior_gamma_15_5 <- prior(gamma(1.5, 5), class = "nu")
prior_gamma_2_5 <- prior(gamma(2, 5), class = "nu")
prior_half_normal_5 <- prior(normal(0, 10), class = "nu", lb = 0)
prior_half_normal_10 <- prior(normal(0, 10), class = "nu", lb = 0)
prior_half_cauchy <- prior(cauchy(0, 5), class = "nu", lb = 0)
```

With our simulated data, with $\nu$'s of $2,3,\ldots, 25$ we can create posterior distributions as follows:

```{r}
#| label: posterior_estimates_test
#| echo: true
#| warning: false
# fit1 <- brm(
#   nu_22 ~ 1,
#   data = dat_100,
#   family = student(),
#   prior = c(
#     prior_uniform_1_50,
#     prior(exponential(1), class = "sigma")
#   ),
#   warmup = 1000,
#   iter = 11000,
#   chains = 4
# )

# post_nu1 <- as_draws_df(fit1)$nu
# plot(fit1)$nu
# mean(post_nu1)

# summary(fit1)
```

Sample size of 100


```{r}
#| label: posterior_draws_unif(1_50)
#| echo: true
#| warning: false

set.seed(502)
fits_uniform_prior_a <- dat_100 |>
  map(function(x) {
    temp_data <- data.frame(y = x)

    brm(
      y ~ 1,
      data = temp_data,
      family = student(),
      prior = c(
        prior_uniform_1_50,
        prior(exponential(1), class = "sigma")
      ),
      warmup = 1000,
      iter = 11000,
      chains = 4
    )
  })

# fits_uniform_prior_a |> map(\(x) plot(x))
# fits_uniform_prior_a |> map(\(x) summary(x))

saveRDS(fits_uniform_prior_a, "Unif_1_50_100.rds")
```

```{r}
#| label: posterior_draws_gamma_1a
#| echo: true
#| warning: false
#gamma(1,4)
set.seed(502)
fits_gamma_prior_1a <- dat_100 |>
  map(function(x) {
    temp_data <- data.frame(y = x)

    brm(
      y ~ 1,
      data = temp_data,
      family = student(),
      prior = c(
        prior_gamma_1_4,
        prior(exponential(1), class = "sigma")
      ),
      warmup = 1000,
      iter = 11000,
      chains = 4
    )
  })

# fits_gamma_prior_1a |> map(\(x) plot(x))
# fits_gamma_prior_1a |> map(\(x) summary(x))

saveRDS(fits_gamma_prior_1a, "Gamma_1_4_100.rds")
```

```{r}
#| label: posterior_draws_gamma_2a
#| echo: true
#| warning: false
#gamma(1.5,5)
set.seed(502)
fits_gamma_prior_2a <- dat_100 |>
  map(function(x) {
    temp_data <- data.frame(y = x)

    brm(
      y ~ 1,
      data = temp_data,
      family = student(),
      prior = c(
        prior_gamma_15_5,
        prior(exponential(1), class = "sigma")
      ),
      warmup = 1000,
      iter = 11000,
      chains = 4
    )
  })

# fits_gamma_prior_2a |> map(\(x) plot(x))
# fits_gamma_prior_2a |> map(\(x) summary(x))

saveRDS(fits_gamma_prior_2a, "Gamma_1_5_5_100.rds")
```


```{r}
#| label: posterior_draws_gamma_3a
#| echo: true
#| warning: false
#gamma(2,5)
set.seed(502)
fits_gamma_prior_3a <- dat_100 |>
  map(function(x) {
    temp_data <- data.frame(y = x)

    brm(
      y ~ 1,
      data = temp_data,
      family = student(),
      prior = c(
        prior_gamma_2_5,
        prior(exponential(1), class = "sigma")
      ),
      warmup = 1000,
      iter = 11000,
      chains = 4
    )
  })
# fits_gamma_prior_3a |> map(\(x) plot(x))
# fits_gamma_prior_3a |> map(\(x) summary(x))

saveRDS(fits_gamma_prior_3a, "Gamma_2_5_100.rds")
```

```{r}
#| label: posterior_draws_half_normal_1a
#| echo: true
#| warning: false

set.seed(502)
fits_half_normal_1a <- dat_100 |>
  map(function(x) {
    temp_data <- data.frame(y = x)

    brm(
      y ~ 1,
      data = temp_data,
      family = student(),
      prior = c(
        prior_half_normal_5,
        prior(exponential(1), class = "sigma")
      ),
      warmup = 1000,
      iter = 11000,
      chains = 4
    )
  })

# fits_half_normal_1a |> map(\(x) plot(x))
# fits_half_normal_1a |> map(\(x) summary(x))

saveRDS(fits_half_normal_1a, "Half_Normal_0_5_100.rds")
```

```{r}
#| label: posterior_draws_half_normal_2a
#| echo: true
#| warning: false

set.seed(502)
fits_half_normal_2a <- dat_100 |>
  map(function(x) {
    temp_data <- data.frame(y = x)

    brm(
      y ~ 1,
      data = temp_data,
      family = student(),
      prior = c(
        prior_half_normal_10,
        prior(exponential(1), class = "sigma")
      ),
      warmup = 1000,
      iter = 11000,
      chains = 4
    )
  })

# fits_half_normal_2a |> map(\(x) plot(x))
# fits_half_normal_2a |> map(\(x) summary(x))

saveRDS(fits_half_normal_2a, "Half_Normal_0_10_100.rds")
```

```{r}
#| label: posterior_draws_half_cauchy_a
#| echo: true
#| warning: false

set.seed(502)
fits_half_cauchy_a <- dat_100 |>
  map(function(x) {
    temp_data <- data.frame(y = x)

    brm(
      y ~ 1,
      data = temp_data,
      family = student(),
      prior = c(
        prior_half_cauchy,
        prior(exponential(1), class = "sigma")
      ),
      warmup = 1000,
      iter = 11000,
      chains = 4
    )
  })

# fits_half_cauchy_a |> map(\(x) plot(x))
# fits_half_cauchy_a |> map(\(x) summary(x))

saveRDS(fits_half_cauchy_a, "Half_Cauchy_0_5_100.rds")
```

Sample size of 1000

```{r}
#| label: posterior_draws_unif_b
#| echo: true
#| warning: false

set.seed(502)
fits_uniform_prior_b <- dat_1000 |>
  map(function(x) {
    temp_data <- data.frame(y = x)

    brm(
      y ~ 1,
      data = temp_data,
      family = student(),
      prior = c(
        prior_uniform_1_50,
        prior(exponential(1), class = "sigma")
      ),
      warmup = 1000,
      iter = 11000,
      chains = 4
    )
  })

# fits_uniform_prior_b |> map(\(x) plot(x))
# fits_uniform_prior_b |> map(\(x) summary(x))

saveRDS(fits_uniform_prior_b, "Unif_1_50_1000.rds")
```

```{r}
#| label: posterior_draws_gamma_1b
#| echo: true
#| warning: false
#gamma(1,4)
set.seed(502)
fits_gamma_prior_1b <- dat_1000 |>
  map(function(x) {
    temp_data <- data.frame(y = x)

    brm(
      y ~ 1,
      data = temp_data,
      family = student(),
      prior = c(
        prior_gamma_1_4,
        prior(exponential(1), class = "sigma")
      ),
      warmup = 1000,
      iter = 11000,
      chains = 4
    )
  })

# fits_gamma_prior_1b |> map(\(x) plot(x))
# fits_gamma_prior_1b |> map(\(x) summary(x))

saveRDS(fits_gamma_prior_1b, "Gamma_1_4_1000.rds")
```

```{r}
#| label: posterior_draws_gamma_2b
#| echo: true
#| warning: false
#gamma(1.5,5)
set.seed(502)
fits_gamma_prior_2b <- dat_1000 |>
  map(function(x) {
    temp_data <- data.frame(y = x)

    brm(
      y ~ 1,
      data = temp_data,
      family = student(),
      prior = c(
        prior_gamma_15_5,
        prior(exponential(1), class = "sigma")
      ),
      warmup = 1000,
      iter = 11000,
      chains = 4
    )
  })

# fits_gamma_prior_2b |> map(\(x) plot(x))
# fits_gamma_prior_2b |> map(\(x) summary(x))

saveRDS(fits_gamma_prior_2b, "Gamma_1_5_5_1000.rds")
```


```{r}
#| label: posterior_draws_gamma_3b
#| echo: true
#| warning: false
#gamma(2,5)
set.seed(502)
fits_gamma_prior_3b <- dat_1000 |>
  map(function(x) {
    temp_data <- data.frame(y = x)

    brm(
      y ~ 1,
      data = temp_data,
      family = student(),
      prior = c(
        prior_gamma_2_5,
        prior(exponential(1), class = "sigma")
      ),
      warmup = 1000,
      iter = 11000,
      chains = 4
    )
  })

# fits_gamma_prior_3b |> map(\(x) plot(x))
# fits_gamma_prior_3b |> map(\(x) summary(x))

saveRDS(fits_gamma_prior_3b, "Gamma_2_5_1000.rds")
```

```{r}
#| label: posterior_draws_half_normal_1b
#| #| echo: true
#| warning: false

set.seed(502)
fits_half_normal_1b <- dat_1000 |>
  map(function(x) {
    temp_data <- data.frame(y = x)

    brm(
      y ~ 1,
      data = temp_data,
      family = student(),
      prior = c(
        prior_half_normal_5,
        prior(exponential(1), class = "sigma")
      ),
      warmup = 1000,
      iter = 11000,
      chains = 4
    )
  })

# fits_half_normal_1b |> map(\(x) plot(x))
# fits_half_normal_1b |> map(\(x) summary(x))

saveRDS(fits_half_normal_1b, "Half_Normal_0_5_1000.rds")
```

```{r}
#| label: posterior_draws_half_normal_2b
#| echo: true
#| warning: false

set.seed(502)
fits_half_normal_2b <- dat_1000 |>
  map(function(x) {
    temp_data <- data.frame(y = x)

    brm(
      y ~ 1,
      data = temp_data,
      family = student(),
      prior = c(
        prior_half_normal_10,
        prior(exponential(1), class = "sigma")
      ),
      warmup = 1000,
      iter = 11000,
      chains = 4
    )
  })

# fits_half_normal_2b |> map(\(x) plot(x))
# fits_half_normal_2b |> map(\(x) summary(x))

saveRDS(fits_half_normal_2b, "Half_Normal_0_10_1000.rds")
```

```{r}
#| label: posterior_draws_half_cauchy_b
#| echo: true
#| warning: false

set.seed(502)
fits_half_cauchy_b <- dat_1000 |>
  map(function(x) {
    temp_data <- data.frame(y = x)

    brm(
      y ~ 1,
      data = temp_data,
      family = student(),
      prior = c(
        prior_half_cauchy,
        prior(exponential(1), class = "sigma")
      ),
      warmup = 1000,
      iter = 11000,
      chains = 4
    )
  })

# fits_half_cauchy_b |> map(\(x) plot(x))
# fits_half_cauchy_b |> map(\(x) summary(x))

saveRDS(fits_half_cauchy_b, "Half_Cauchy_0_5_1000.rds")
```

Sample size 10000

```{r}
#| label: posterior_draws_c
#| echo: true
#| warning: false

set.seed(502)
fits_uniform_prior_c <- dat_10000 |>
  map(function(x) {
    temp_data <- data.frame(y = x)

    brm(
      y ~ 1,
      data = temp_data,
      family = student(),
      prior = c(
        prior_uniform_1_50,
        prior(exponential(1), class = "sigma")
      ),
      warmup = 1000,
      iter = 11000,
      chains = 4
    )
  })

# fits_uniform_prior_c |> map(\(x) plot(x))
# fits_uniform_prior_c |> map(\(x) summary(x))

saveRDS(fits_uniform_prior_c, "Unif_1_50_10000.rds")
```

```{r}
#| label: posterior_draws_gamma_1c
#| echo: true
#| warning: false
#gamma(1,4)

set.seed(502)
fits_gamma_prior_1c <- dat_10000 |>
  map(function(x) {
    temp_data <- data.frame(y = x)

    brm(
      y ~ 1,
      data = temp_data,
      family = student(),
      prior = c(
        prior_gamma_1_4,
        prior(exponential(1), class = "sigma")
      ),
      warmup = 1000,
      iter = 11000,
      chains = 4
    )
  })

# fits_gamma_prior_1c |> map(\(x) plot(x))
# fits_gamma_prior_1c |> map(\(x) summary(x))

saveRDS(fits_gamma_prior_1c, "Gamma_1_4_10000.rds")
```

```{r}
#| label: posterior_draws_gamma_2c
#| echo: true
#| warning: false
#gamma(1.5,5)

set.seed(502)
fits_gamma_prior_2c <- dat_10000 |>
  map(function(x) {
    temp_data <- data.frame(y = x)

    brm(
      y ~ 1,
      data = temp_data,
      family = student(),
      prior = c(
        prior_gamma_15_5,
        prior(exponential(1), class = "sigma")
      ),
      warmup = 1000,
      iter = 11000,
      chains = 4
    )
  })

# fits_gamma_prior_2c |> map(\(x) plot(x))
# fits_gamma_prior_2c |> map(\(x) summary(x))

saveRDS(fits_gamma_prior_2c, "Gamma_1_5_5_10000.rds")
```


```{r}
#| label: posterior_draws_gamma_3c
#| echo: true
#| warning: false
#gamma(2,5)
set.seed(502)
fits_gamma_prior_3c <- dat_10000 |>
  map(function(x) {
    temp_data <- data.frame(y = x)

    brm(
      y ~ 1,
      data = temp_data,
      family = student(),
      prior = c(
        prior_gamma_2_5,
        prior(exponential(1), class = "sigma")
      ),
      warmup = 1000,
      iter = 11000,
      chains = 4
    )
  })

# fits_gamma_prior_3c |> map(\(x) plot(x))
# fits_gamma_prior_3c |> map(\(x) summary(x))

saveRDS(fits_gamma_prior_3c, "Gamma_2_5_10000.rds")
```

```{r}
#| label: posterior_draws_half_normal_1c
#| echo: true
#| warning: false

set.seed(502)
fits_half_normal_1c <- dat_10000 |>
  map(function(x) {
    temp_data <- data.frame(y = x)

    brm(
      y ~ 1,
      data = temp_data,
      family = student(),
      prior = c(
        prior_half_normal_5,
        prior(exponential(1), class = "sigma")
      ),
      warmup = 1000,
      iter = 11000,
      chains = 4
    )
  })

# fits_half_normal_1c |> map(\(x) plot(x))
# fits_half_normal_1c |> map(\(x) summary(x))

saveRDS(fits_half_normal_1c, "Half_Normal_0_5_10000.rds")
```

```{r}
#| label: posterior_draws_half_normal_2c
#| echo: true
#| warning: false

set.seed(502)
fits_half_normal_2c <- dat_10000 |>
  map(function(x) {
    temp_data <- data.frame(y = x)

    brm(
      y ~ 1,
      data = temp_data,
      family = student(),
      prior = c(
        prior_half_normal_10,
        prior(exponential(1), class = "sigma")
      ),
      warmup = 1000,
      iter = 11000,
      chains = 4
    )
  })

# fits_half_normal_2c |> map(\(x) plot(x))
# fits_half_normal_2c |> map(\(x) summary(x))

saveRDS(fits_half_normal_2c, "Half_Normal_0_10_10000.rds")
```

```{r}
#| label: posterior_draws_half_cauchy_c
#| echo: true
#| warning: false

set.seed(502)
fits_half_cauchy_c <- dat_10000 |>
  map(function(x) {
    temp_data <- data.frame(y = x)

    brm(
      y ~ 1,
      data = temp_data,
      family = student(),
      prior = c(
        prior_half_cauchy,
        prior(exponential(1), class = "sigma")
      ),
      warmup = 1000,
      iter = 11000,
      chains = 4
    )
  })

# fits_half_cauchy_c |> map(\(x) plot(x))
# fits_half_cauchy_c |> map(\(x) summary(x))

saveRDS(fits_half_cauchy_c, "Half_Cauchy_0_5_10000.rds")
```



```{r}
#| label: analyzing_dumb_shit
#| echo: true
#| eval: false


gamma_post_14_100 <- readRDS("Code/Gamma_1_4_100.rds")
gamma_post_14_1000 <- readRDS("Code/Gamma_1_4_1000.rds")
gamma_post_14_10000 <- readRDS("Code/Gamma_1_4_10000.rds")

```

