---
title: "MCMC Code for sampling from posterior t distribution"
author: "Eric Folsom"
format: pdf
---

```{r}
#| label: setup
#| echo: true
#| warning: false
library(tidyverse)
library(brms)
library(janitor)
set.seed(502)
```

We are trying to create a posterior distribution for the degrees of freedom from a $t$ distribution. We can set up our model as follows:

Our likelihood, or sampling distribution is:

$$
p(y_i | t) \sim t(\nu)
$$


For our prior we have a couple of choices:
$$
p(\nu) \sim \text{Some strictly positive distribution}
$$

For our prior for $\nu$ we will try the following:

$$
p(\nu) \sim \text{Uniform}(0,\theta) \text{with various choices of } \theta
$$

$$
p(\nu)\sim N^+(0,\sigma^2) \quad \text{with various choices of } \sigma^2
$$

$$
p(\nu)\sim \text{Gamma}(\alpha, \beta) \text{with various choices of } \alpha \text{ and } \beta
$$

$$
p(\nu)\sim \text{Cauchy}^+() 
$$

Thus our model for our posterior, $P(\nu | y_i)$ will be 

$$
P(\nu|y_i)\propto p(\mathbf{y} | \nu) p(\nu)
$$


We can generate data from $t$-distributions with various degrees of freedom ($\nu$) as follows:

```{r}
#| label: example_data
#| echo: true
#| warning: false
sim_dat <- function(nsims, nu) {
  cols <- nu |>
    map(function(nu) {
      rt(nsims, nu)
    })

  names(cols) <- paste0("nu_", nu)

  data <- as.data.frame(cols) |> mutate(mu0 = rep(0, nsims))

  return(data)
}
nu <- sample(c(2:25), 5, replace = F)
n <- 10000
dat <- sim_dat(n, nu)
```

With our simulated data, with $\nu$'s of $2,3,\ldots, 25$ we can create posterior distributions as follows:

```{r}
#| label: posterior_estimates_test
#| echo: true
#| warning: false



fit1 <- brm(
  nu_8 ~ 1,
  data = dat,
  family = student(),
  prior = c(
    prior(uniform(1, 10), class = "nu", lb = 1, ub = 10),
    prior(exponential(1), class = "sigma")
  ),
  warmup = 1000,
  iter = 4000,
  chains = 4
)

post_nu1 <- as_draws_df(fit1)$nu
plot(fit1)$nu
mean(post_nu1)

summary(fit1)
```

```{r}
#| label: posterior_draws_unif(1_50)
#| echo: true
#| warning: false



nu_to_try <- names(dat)

 
fits_uniform_prior <- dat |> map(function(x){
    
    temp_data <- data.frame(y = x)

    brm(
    y ~ 1,
    data = temp_data,
    family = student(),
    prior = c(
        prior(uniform(1, 50), class = "nu", lb = 1, ub = 50),
        prior(exponential(1), class = "sigma")
    ),
    warmup = 1000,
    iter = 4000,
    chains = 4
    )

}
 )
```

```{r}
#| label: posterior_draws_gamma
#| echo: true
#| warning: false



nu_to_try <- names(dat)

 
fits_gamma_prior <- dat |> map(function(x){
    
    temp_data <- data.frame(y = x)

    brm(
    y ~ 1,
    data = temp_data,
    family = student(),
    prior = c(
        prior(uniform(1, 50), class = "nu", lb = 1, ub = 50),
        prior(exponential(1), class = "sigma")
    ),
    warmup = 1000,
    iter = 4000,
    chains = 4
    )

}
 )
```
